Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-20 ms.tex
hi

\begin{document}
\title{Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
\maketitle

\begin{abstract}
We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole mass $M_{\bullet}$, parameterized gas heating rate, and observationally-motivated stellar density profiles.  Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated primarily by stellar winds, supernovae, and black hole feedback.  Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole mass accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.  We assess the conditions under which radiative instabilities will develop absent black hole feedback, based on the heating supplied by the average star formation history for galaxies corresponding to a given black hole mass.  Results for the average accretion rate, as well as the maximum thermally-stable and -unstable accretion rates, are compared to the nuclear X-ray luminosities of a sample of quiescent black holes.  We determine that the measured high accretion rates and short growth times of low mass black holes in the local universe must be the result of an external gas supply, rather than secular processes resulting from stellar mass loss within the galactic nucleus.  We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.
\end{abstract}

>>>>

\begin{document}
\title{Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes}
\maketitle

\begin{abstract}
We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of nominally quiescent galaxies for a range of central black hole mass $M_{\bullet}$, parameterized gas heating rate, and observationally-motivated stellar density profiles.  Mass is supplied to the circumnuclear medium by stellar winds, while gas is heated primarily by stellar winds, supernovae, and black hole feedback.  Analytic estimates are provided for the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole mass accretion rate, $\dot{M}$, as a function of black hole mass and the gas heating efficiency, the latter of which is related to the star-formation history.  We assess the conditions under which radiative instabilities develop, separately in the case of a single burst of star formation and in the case of the average star formation history of galaxies hosting a given black hole mass.  The nuclear X-ray luminosities of a sample of quiescent black holes are combined with our results for $\dot{M}$ and an estimate of the radiative efficiency of the accretion flow to conclude that quiescent black holes in the local universe are consistent with accreting in a locally thermally-stable state.  The maximum accretion rate of a thermally-stable flow is, however, too low to explain the accretion rates and short growth time of low mass black holes in the local universe.  The latter must instead result from gas being fed in from large radii, either due to galaxy mergers associated with hierarchical growth or thermal instabilities on larger (galactic) scales.  
The accretion rate estimated in the latter case, as well as the maximum thermally-stable and thermal-unstable rates, are compared to the nuclear X-ray luminosities of a sample of quiescent black holes.  We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.
\end{abstract}
